Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-22 latex/article.tex
wip

\begin{figure}[!htbp]
  \begin{center}
    \subfigure{}{\includegraphics[width=\textwidth]{figs/morton}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
  \end{center}
\caption{Morton codes associated to cells of a linear quatree. Each
   morton code of a child cell is obtained by adding a suffix to its
  parent code \emph{(left)}. The adaptive representation consists of
  quadtree cells whose depth is view point dependent
  \emph{(middle)}. Finally, adaptive Marching-Cubes is used to
  generate the triangulation \emph{(right)}.}
\label{fig_quadtree_partitionning}
\end{figure}

@@

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to prevent refining cells outside the camera frustrum. Using a criterion based on the distance between a cell and the camera is well suited to GPU since it can be evaluated independently on all cells. Hence, we can efficiently determine if a cell must be subdivided or not. Figure \ref{fig_lod_octree}
illustrates the level of details (LoD for short) criterion we
use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
angle, an object at distance $d$ from the camera with diameter greater than
 $2\cdot d\cdot\tan(\alpha)$
 is projected into more than one pixel
(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
criterion is based on the ratio (\emph{visibility ratio} in the
following)between the cell diameter $l(c)$ (power of 2 depending on
the depth), and
$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
split and merge decision are based on this visibility ratio:
\begin{itemize}
\item $c$ is split if its children cells have a visibility ratio
  greater than  constant $k$\,;
\item $c$ and its sibling cells are merged if their parent cell $c'$
  have av visibility ratio lower than $k$\;
\item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=4cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=4cm]{viewlod2_small}~~~~~
    \includegraphics[width=3.5cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
    angular criterion \emph{(middle)}. Based on LoD criterion
    evaluation, the cell buffer is
  updated between each frame \emph{(right)}.}
  \label{fig_lod_octree}
\end{figure}
%
In addition to the distance criterion, we add an angular term in order
to prevent subdivision of cells far from the camera frustrum (see
Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
details but please note that stay, split and merge decisions of all cells are computed in
parallel from all cell morton codes.

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
  \end{center}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
  \label{fig:approx2}
\end{figure}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{@{}lrrrrrr@{}}
      \toprule
    Quantities & H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches & & & & & &\\
      Time (in ms) & & & & & &\\
      $L_\infty$ error (\wrt $l_0$) & & & & & &\\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{object, size, radius, full res, num of vertices (timings
    only consider the curvature estimation step).\label{tab:full-res-stat}}
\end{table}

>>>>

\begin{figure}[!htbp]
  \begin{center}
    \subfigure{}{\includegraphics[width=0.9\textwidth]{figs/morton}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
  \end{center}
\caption{Morton codes associated to cells of a linear quatree. Each
   morton code of a child cell is obtained by adding a suffix to its
  parent code \emph{(left)}. The adaptive representation consists of
  quadtree cells whose depth is view point dependent
  \emph{(middle)}. Finally, adaptive Marching-Cubes is used to
  generate the triangulation \emph{(right)}.}
\label{fig_quadtree_partitionning}
\end{figure}

@@

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to prevent refining cells outside the camera frustrum. Using a criterion based on the distance between a cell and the camera is well suited to GPU since it can be evaluated independently on all cells. Hence, we can efficiently determine if a cell must be subdivided or not. Figure \ref{fig_lod_octree}
illustrates the level of details (LoD for short) criterion we
use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
angle, an object at distance $d$ from the camera with diameter greater than
 $2\cdot d\cdot\tan(\alpha)$
 is projected into more than one pixel
(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
criterion is based on the ratio (\emph{visibility ratio} in the
following)between the cell diameter $l(c)$ (power of 2 depending on
the depth), and
$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
split and merge decision are based on this visibility ratio:
\begin{itemize}
\item $c$ is split if its children cells have a visibility ratio
  greater than  constant $k$\,;
\item $c$ and its sibling cells are merged if their parent cell $c'$
  have av visibility ratio lower than $k$\;
\item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=3.5cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=3.5cm]{viewlod2_small}~~~~~
    \includegraphics[width=3cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
    angular criterion \emph{(middle)}. Based on LoD criterion
    evaluation, the cell buffer is
  updated between each frame \emph{(right)}.}
  \label{fig_lod_octree}
\end{figure}
%
In addition to the distance criterion, we add an angular term in order
to prevent subdivision of cells far from the camera frustrum (see
Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
details but please note that stay, split and merge decisions of all cells are computed in
parallel from all cell morton codes.

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-bh}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-ada}}
  \end{center}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
  \label{fig:approx2}
\end{figure}

@@

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step.

\begin{table}
  \begin{center}
    \begin{tabular}{@{}lrrrrrrrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=$}   & \multicolumn{6}{c}{$R=$}\\
      \cmidrule(r){2-12}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches & & & & & & & & & & & &\\
      Time (in ms) & & & & & && & & & & &\\
      $L_\infty$ error (\wrt $l_0$) & & & & & && & & & & &\\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{object, size, radius, full res, num of vertices (timings
    only consider the curvature estimation step).\label{tab:full-res-stat}}
\end{table}
